Increasing quality of self-recovering images using BPCS Steganography

### 2014-11-03 Paper/main.tex
Section 2 proof read

\noindent 
Many current self-recovering image methods exist, however few of the current methods provide good quality images after embedding as well as after reconstruction.
This is due to an inherent trade off between the amount of information that can be embedded into an image and the quality of the image after embedding.
This dissertation proposes a novel method for increasing the quality of the image after embedding as well as the quality of the image after reconstruction in self-recovering images using the BPCS Steganography algorithm for content embedding as well as employing a fragile watermark for detecting image modifications.
Experimental results show that the proposed method achieves a good quality image after embedding as well as a good quality image after reconstruction when compared to some of the currently available self-recovering image methods.

@@

\hspace{0pt} \\
The proposed method uses steganography to embed the information into an image in a way that is not easily visibly detectable by a human observer.
A successful steganographic method has certain characteristics according to literature:
\begin{itemize}
	\item Invisibility: The invisibility of a steganographic algorithm is very important. The strength of steganography lies in its ability to be unnoticed by the human eye. If one can see that an image has been tampered with then invisibility has been lost and the algorithm has been compromised \cite{morkel2005overview}.
	\item Robustness: The resistance to various image processing methods, compression and other image modifications. Thus how much of the image can be modified without destroying the embedded content \cite{cheddad2010digital}.
	\item Capacity: The maximum number of bits that can be embedded into an image without introducing statistically or visually detectable artifacts \cite{fridrich2009steganography}.
\end{itemize}
Least significant bit embedding (LSB) is a steganographic method that can be used to embed information. 
LSB works by replacing the least significant bit (or \textit{n} least significant bits) of an image colour value with a binary bit from a message. The least significant bit of a colour value is the binary bit that carries the least value and thus the change in colour is not perceptible to the human eye.
LSB embedding is the most common and easiest method for embedding messages in an image \cite{lee2000high}, and many methods exist for detecting the hidden information

\hspace{0pt} \\
Bit plane complexity steganography (BPCS) is another steganographic embedding method that was developed in 1999 by E. Kawaguchi and R.O. Eason \cite{kawaguchi1999principles}. 
The goal of the BPCS algorithm is to embed as much data as possible into a cover image while maintaining invisibility \cite{beaullieubpcs}.

@@

\subsection{Self embedding and recovery}
\label{introSelfEmbedRecovery}
Self-embedding is a scheme where image content is embedded into the image itself \cite{fridrich1999images}. The embedded content can then later be used to recover damaged or modified parts of the image without accessing the original image itself.
self-embedding is also referred to as self-recovering
A self-recovery scheme such as the proposed method contains a couple of high level steps.
Firstly an approximation of the original image, referred to as the image reference content, is embedded into the original image along with a fragile watermark.
The resulting image is referred to as the image after embedding.
The watermark helps to determine which parts of the image after embedding was modified if any (see \ref{introFragWatermarking}).
When the authentic image needs to be reconstructed, after modification, the fragile watermark is used to determine which areas of the image were modified.
An attempt is then made to extract the areas that were modified from the original image and replace the tampered areas with the extracted information.
If this process is successful the user is left with a high quality reconstruction of the original image.

@@

\subsubsection{Image authentication}
\label{extractionAuthentication}
The first step for the image extraction and reconstruction process is to determine which, if any, parts of the image after embedding has been tampered with.
This is accomplished by first completing steps 1-4 of the BPCS steg algorithm (\ref{bpcsSteg}).
For each section (section refers here to 8x8 pixel section, thus a section here contains all 8 bit planes) the authentication hash string is calculated as described in \ref{impFragileWatermark}. 
The embedded hash is then extracted from the LSB plane of that block and compared to the calculated hash to determine if they match, in which case the section can be seen as tamper-free.
If they do not match then that section has been tampered with and needs to be reconstructed.

>>>>

\noindent 
Many current self-recovering image methods exist, however few of the current methods provide good quality images after embedding as well as after reconstruction.
This is due to an inherent trade off between the amount of information that can be embedded into an image and the quality of the image after embedding.
This dissertation proposes a novel method for increasing the quality of the image after embedding as well as the quality of the image after reconstruction in self-recovering images using the BPCS steganography algorithm for content embedding as well as employing a fragile watermark for detecting image modifications.
Experimental results show that the proposed method achieves a good quality image after embedding as well as a good quality image after reconstruction when compared to some of the currently available self-recovering image methods.

@@

\hspace{0pt} \\
The proposed method uses steganography to embed the information into an image in a way that is not easily visibly detectable by a human observer.
A successful steganographic method has certain characteristics according to literature:
\begin{itemize}
	\item Invisibility: The invisibility of a steganographic algorithm is very important. The strength of steganography lies in its ability to be unnoticed by the human eye. If one can see that an image has been tampered with then invisibility has been lost and the algorithm has been compromised \cite{morkel2005overview}.
	\item Robustness: The resistance to various image processing methods, compression and other image modifications. Thus how much of the image can be modified without destroying the embedded content \cite{cheddad2010digital}.
	\item Capacity: The maximum number of bits that can be embedded into an image without introducing statistically or visually detectable artifacts \cite{fridrich2009steganography}.
\end{itemize}
Least significant bit embedding (LSB) is a steganographic method that can be used to embed information. 
LSB works by replacing the least significant bit (or \textit{n} least significant bits) of an image colour value with a binary bit from a message. The least significant bit of a colour value is the binary bit that carries the least value and thus the change in colour is not perceptible to the human eye.
LSB embedding is the most common and easiest method for embedding messages in an image \cite{lee2000high}, and many methods exist for detecting the hidden information.

\hspace{0pt} \\
Bit plane complexity segmentation (BPCS) is another steganographic embedding method that was developed in 1999 by E. Kawaguchi and R.O. Eason \cite{kawaguchi1999principles}. 
The goal of the BPCS algorithm is to embed as much data as possible into a cover image while maintaining invisibility \cite{beaullieubpcs}.

@@

\subsection{Self embedding and recovery}
\label{introSelfEmbedRecovery}
Self-embedding is a scheme where image content is embedded into the image itself \cite{fridrich1999images}. The embedded content can then later be used to recover damaged or modified parts of the image without accessing the original image itself.
self-embedding is also referred to as self-recovering.
A self-recovery scheme such as the proposed method contains a couple of high level steps.
Firstly an approximation of the original image, referred to as the image reference content, is embedded into the original image along with a fragile watermark.
The resulting image is referred to as the image after embedding.
The watermark helps to determine which parts of the image after embedding was modified if any (see \ref{introFragWatermarking}).
When the authentic image needs to be reconstructed, after modification, the fragile watermark is used to determine which areas of the image were modified.
An attempt is then made to extract the areas that were modified from the original image and replace the tampered areas with the extracted information.
If this process is successful the user is left with a high quality reconstruction of the original image.

@@

\subsubsection{Image authentication}
\label{extractionAuthentication}
The first step for the image extraction and reconstruction process is to determine which, if any, parts of the image after embedding has been tampered with.
This is accomplished by first completing steps 1-4 of the BPCS steganography algorithm (\ref{bpcsSteg}).
For each section (section refers here to 8x8 pixel section, thus a section here contains all 8 bit planes) the authentication hash string is calculated as described in \ref{impFragileWatermark}. 
The embedded hash is then extracted from the LSB plane of that block and compared to the calculated hash to determine if they match, in which case the section can be seen as tamper-free.
If they do not match then that section has been tampered with and needs to be reconstructed.
